\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/background.tex
fix ref in intro/bg

%\noindent\outline{HID Protocol}\\
Right after one year of the appearance of USB 1.0, a standard named HID (Human
Interface Device)\hongyi{Citation Needed} was born based on USB. HID is
designed with to unify the implementation for devices like mouse,
keyboard, etc. Before its appearance, the standard is divided between
manufacturers, for example, the mouse of Company A may use X-Y coordinates to
represent its location while the mouse of Company B uses relative displacement.
This means every device needs its own drivers to work. After HID, people just
write one driver for an entire class of HIDs. Furthermore, HID standard also
requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed
convenient but insecure too.

@@

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called USB Type-C is introduced in 2013 by USB-IF\fengwei{Need a
citation}. As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
D-). The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers USB packets.

%\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered. As
the USB-IF believes it is the duty of original equipment manufacturers (OEMs)
to decide whether security features should be implemented.\hongyi{Citation
needed}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

\fengwei{FIXME: add a reference for each attack in the Table.}
\begin{table*}
\begin{tabular}{|c|c|c|c|c|}
	\hline
	Year & Protocol Version & Supported Peripherals & Transfer Speed & Attacks \\
	\hline
	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB)~\cite{badusb} \\
	\hline
	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming Attack~\cite{JFC,JFCImpact} \\
	\hline
	2008 & USB 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
	\hline
	2013 & USB 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
	\hline
	2017 & USB 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
	\hline
\end{tabular}
	\linebreak
\caption{USB Protocol Timeline}
\label{table:usb_timeline}
\end{table*}

>>>>

%\noindent\outline{HID Protocol}\\
Right after one year of the appearance of USB 1.0, a standard named HID (Human
Interface Device)~\cite{hid} was born based on USB. HID is
designed with to unify the implementation for devices like mouse,
keyboard, etc. Before its appearance, the standard is divided between
manufacturers, for example, the mouse of Company A may use X-Y coordinates to
represent its location while the mouse of Company B uses relative displacement.
This means every device needs its own drivers to work. After HID, people just
write one driver for an entire class of HIDs. Furthermore, HID standard also
requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed
convenient but insecure too.

@@

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF. As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
D-). The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers USB packets.

%\noindent\outline{Security Problem}\\
During the development of USB specification, security was rarely considered. As
the USB-IF believes it is the duty of original equipment manufacturers (OEMs)
to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

%\fengwei{FIXME: add a reference for each attack in the Table.}
\begin{table*}
\begin{tabular}{|c|c|c|c|c|}
	\hline
	Year & Protocol Version & Supported Peripherals & Transfer Speed & Attacks \\
	\hline
	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB)~\cite{badusb} \\
	\hline
	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming Attack~\cite{JFC,JFCImpact} \\
	\hline
	2008 & USB 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
	\hline
	2013 & USB 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
	\hline
	2017 & USB 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
	\hline
\end{tabular}
	\linebreak
\caption{USB Protocol Timeline}
\label{table:usb_timeline}
\end{table*}
